\section{Elements And Pads}

Pads represent ports on an element, and can be of two types:
source pads and sink pads. To link two elements you call the
type-overloaded connect function on the two pads. 

Pads are specialized on type; that is, a Source<T> and a Sink<T>
can be connected, but a Source<T1> and Sink<T2> cannot be connected. 

Pads are ``owned'' by their containing element, but said element
only has a pointer to the pad; at construction the element
must create the pad with : 


element::createSourcePad<type_x>("name")
element::createSinkPad<type_x>("name")

This has the advantage of allowing registration with the element, such
that you can ask an element ``give me all your sources'' and ``give me
all your sinks''. 

\subsection{Output Pad Details}
An output pad is created with a reference to a std::list<T>, which
where T is the pad's specialized type. 

then the elements themselves are accessable via: 

getAvailableSources()

getInput<type_x>(name)

getAvailableOutputs()
getOutput<type_x>(name)

Now, each input pad exposes several signals such as newData() and invalidate()
as well as providing a queueview-like interface where you can request chunks of
data for the element. FOR THE ELEMENT. 

------------------------------------------------------------------------------------
The output pad, when connected to an input pad, creates a new queueview and
points the input pad to that queueview. 

Wow, this is going to be templated all to heck. 

outputpad.connect(sinkpad) will: 
   sinkpad.setConnection(newQueueView); 
   outputpad.push_back(inputpad)
   

How do we say ``I have the name of output X, what type is it?''? 
Element.getOutput(``name'').getPossibleChildren()

The point is that this knowledge can live in a lot of places. 

\subsection{Pipeline Details}

Each pipeline has: 

Four associated visitors
A pointer to some central source state

a collection of source, filter, sink, and trigger elements

Exposed vis elements, and exposed triggers

Now remember that vis elements are elements which also support the
TriggerRender and StreamRender interfaces, as well as having
a trigger sink named ``triggerSink''

And Triggers are elements with a single source, ``triggerSource''

pipeline::createSource(name)
pipeline::createFilter(name)
pipeline::createTrigger(name)
pipeline::createSink(name)

